Basics of Hardware Cache Optimization

### 2017-05-26 paper.tex
Move .tex files into subdirectory
Add awesome plot, expand content, tweak stuff
Add amazing table and tweak things
Use varioref in addition to hyperref and cleveref
https://ctan.org/pkg/varioref
Shorten some links

% Preamble {{{1
\documentclass[a4paper]{scrartcl}

\usepackage[utf8]{inputenc} % Assume this file is encoded in UTF-8.
\usepackage[T1]{fontenc}    % Don't fake umlauts etc.
\usepackage{lmodern}        % Use the lmodern font (http://tex.stackexchange.com/a/65103).
\usepackage{microtype}      % Better microtypography (http://www.ctan.org/pkg/microtype)
\usepackage{hyperref}       % Clickable hyperlinks, load before `glossaries`
\usepackage{cleveref}       % Use `\cref{fig:foo}` instead of `figure~\ref{fig:foo}`.
                            % Load after `hyperref`.  See
                            % <https://tex.stackexchange.com/q/36295>
\usepackage{comment}        % Comment out sections of text.
\usepackage{mathtools}      % Improved facilities for typesetting mathematical formulae
\usepackage{dirtytalk}      % ...

@@

% Source code listings with improved syntax highlighting
\usepackage{minted}
\usemintedstyle{pastie}

@@

\makeglossaries
\loadglsentries{glossary}

@@

\input{intro}
\input{motivation}
\input{types}
\input{basic-concepts}

@@

\clearpage
% \appendix
\begin{appendices}
   % See <https://tex.stackexchange.com/q/119513>.
   \crefalias{section}{appsec}
   \input{appendices}
\end{appendices}

>>>>

% Preamble {{{1
% There's some issue that causes captions like "Listing 2.: Foo".  setting the `numbers`
% option like this fixes it.  See <https://tex.stackexchange.com/q/29181>.
\documentclass[a4paper,numbers=noenddot]{scrartcl}

\usepackage[utf8]{inputenc} % Assume this file is encoded in UTF-8.
\usepackage[T1]{fontenc}    % Don't fake umlauts etc.
\usepackage{lmodern}        % Use the lmodern font (http://tex.stackexchange.com/a/65103).
\usepackage{microtype}      % Better microtypography (http://ctan.org/pkg/microtype)
\usepackage{comment}        % Comment out sections of text.
\usepackage{mathtools}      % Improved facilities for typesetting mathematical formulae
\usepackage{dirtytalk}      % ...

% Prevent floats from moving into another section (https://ctan.org/pkg/placeins).
\usepackage[above, below, section]{placeins}

% Stack for cross-referencing.  XXX: the packages have to be loaded in this order (see the
% cleveref manual).
% * The [varioref] package adds commands that automatically print the target's page number
%   iff it is on a different page than the reference.
% * [hyperref] turns references into clickable hyperlinks.
% * Among other things, [cleveref] adds commands that include the type of the referenced
%   object.  Instead of `figure~\ref{fig:foo}`, one can write `\cref{fig:foo}`.  It also
%   enhances the varioref commands accordingly.
% See [1], [2], and [3].
%
% [varioref]: https://ctan.org/pkg/varioref
% [hyperref]: https://ctan.org/pkg/hyperref
% [cleveref]: https://ctan.org/pkg/cleveref
% [1]: https://en.wikibooks.org/wiki/LaTeX/Labels_and_Cross-referencing
% [2]: https://tex.stackexchange.com/q/83037
%      "Difference between ref, varioref and cleveref."
% [3]: https://tex.stackexchange.com/q/36295
%      "Cross-reference packages: which to use, which conflict?"
\usepackage{varioref}
\usepackage{hyperref} % XXX: load before `glossaries`
\usepackage{cleveref} % Use `\cref{fig:foo}` instead of `figure~\ref{fig:foo}`.

% Stack for generating tables from CSV files.  Loading is done by [pgfplotstable].  It can
% also round, format and post-process data.  See [1].
% [siunitx] adds the `S` column type for advanced aligning in tables like around the
% decimal marker.  Getting this to work is a bit tricky; see [2].  There is some support
% for aligning around the decimal marker in [pgfplotstable] (see [3]), but I couldn't get
% it to work.  One can also right-align numbers relatively to each other but still center
% the column as a whole with [siunitx] (see [4]).
% [pgfplotstable]: https://ctan.org/pkg/pgfplotstable
% [siunitx]: https://ctan.org/pkg/siunitx
% [1]: https://tex.stackexchange.com/q/146716
% [2]: https://tex.stackexchange.com/q/131081
% [3]: https://tex.stackexchange.com/q/276485
% [4]: https://tex.stackexchange.com/q/9203
\usepackage{pgfplotstable, siunitx}
% These packages are recommended by [pgfplotstable].  The booktabs package adds the
% `\toprule`, `\midrule`, and `\bottomrule` commands for better looking tables.  See [5].
\usepackage{booktabs, array, colortbl}
% [booktabs]: https://ctan.org/pkg/booktabs
% [5]: https://en.wikibooks.org/wiki/LaTeX/Tables#Professional_tables

% Use a consitent group/thousands separator for siunitx and pgf.
\pgfkeys{/pgf/number format/.cd,
   set thousands separator=\,
}
% \sisetup{
%    group-separator={,}
% }

% Provides the `\captionof` command for typesetting captions outside of floats, which is
% an extension of th one provided by [capt-of](https://ctan.org/pkg/capt-of).  Includes
% the [newfloat package](https://ctan.org/pkg/newfloat), which minted is set up to use.
\usepackage{caption} % See <https://ctan.org/pkg/caption>.
% \captionsetup{labelsep=colon}

@@

% Source code listings with improved syntax highlighting
\usepackage[newfloat]{minted}
\usemintedstyle{pastie}

@@

\makeglossaries
\loadglsentries{tex/glossary}

@@

\input{tex/intro}
\input{tex/motivation}
\input{tex/types}
\input{tex/basic-concepts}

@@

\clearpage
\begin{appendices} % <https://tex.stackexchange.com/q/49643>
   \crefalias{section}{appsec} % See <https://tex.stackexchange.com/q/119513>.
   \crefalias{subsection}{appsec}
   \input{tex/cpu-info}
   \input{tex/methodology}
   \input{tex/data}
   % \input{tex/no-prefetch}
\end{appendices}
